\chapter{推荐阅读：那些关于写作的好书}
\section{必备的书}
American Psychological Association. (2010). Publication manual of the American Psychological Association (6th ed.). Washington, DC: Author.

Merriam-Webster's collegiate dictionary. (11th ed.). (2005). Springfield, MA: Merriam-Webster.

Strunk, W., Jr., \& White, E. B. (2000). The elements of style (4th ed.). New York, NY: Longman.

Zinsser, W. (2001). On writing well (25th anniversary ed.). New York, NY: Quill.



\section{关于文风的书}
Baker, S. (1969). The practical stylist (2nd ed.). New York, NY: Thomas Y. Crowell.

Barzun, J. (2001). Simple and direct: A rhetoric for writers. New York, NY: HarperCollins.

Harris, R. W. (2003). When good people write bad sentences: 12 steps to better writing habits.New York, NY St. Martin's Press.

Smith, K. (2001). Junk English. New York, NY: Blast Books.

Smith, K. (2004) Junk English 2. New York, NY: Blast Books.

Walsh, B. (2000). Lapsing into a comma: A curmudgeon's guide to the many things that can go wrong in print——And how to avoid them. New York, NY: Contemporary Books.

Walsh, B. (2004). The elephants of style: A trunkload of tips on the big issues and gray areas of contemporary American English. New York, NY: McGraw-Hill.




\section{关于语法与标点的书}
Gordon, K. E. (1984). The transitive vampire: A handbook of grammar for the innocent, the eager, and the doomed. New York, NY: Times Books.

Gordon, K. E. (2003). The new well-tempered sentence: A punctuation handbook for the innocent, the eager, and the doomed. Boston, MA: Mariner.

Hale, C. (1999). Sin and syntax: How to craft wickedly effective prose. New York, NY: Broadway.

Truss, L. (2003). Eats, shoots \& leaves: The zero tolerance approach to punctuation. New York, NY: Gotham.




\section{激励写作的书}
Boice, R. (1990). Professor as writers: A self-help guide to productive writing. Stillwater, OK: New Forums Press.

Friedman, B. (1993). Writing past dark: Envy, fear, distraction, and other dilemmas in the writer's life. New York, NY: HarperCollins.

Keyes, R. (2003). The writer's book of hope. New York, NY: Holt.

King, S. (2000). On writing: A memoir of the craft. New York, NY: Scribner.


